---
title: "README"
author: "Derek Beaton & Jeremy Tanuan"
date: "November 25, 2019"
output: github_document
---


**ONDRI Themes**
===================================

Standardized themes, colors, and templates for the ONDRI project's colors and presentations. Developed by Jeremy Tanuan and Derek Beaton.
The package is heavily influenced by and copies key parts of [Karthik Ram's `wesanderson` palette package](https://github.com/karthik/wesanderson).


## **Installation**

Make sure you have [R](https://cran.r-project.org/) and [RStudio](https://www.rstudio.com/products/rstudio/download/). Open RStudio and run the following commands in the RStudio console (the bottom left pane) to install the necessary packages if you have not already done so.

First install the `ondricolors` package
```{r}

if(!require('devtools')){
  devtools::install_github(repo = "dbeaton", subdir = "ONDRIApps/ondricolors")
}


```

Then load the package as 
```{r}
library(ondricolors)
```

You will know that the packages are loaded if the checkbox beside each in the *Packages* tab (the bottom right pane) are checked. Add the checkmark to each for any that are missing from the necessary packages.


## **Palettes**


#### **Cohort1**

```{r} 
ondri_palette("Cohort1")
```

#### **Cohort2**

```{r}
ondri_palette("Cohort2")
```

## **Plots**

```{r}
## continuous example
pal <- ondri_palette("Cohort1", start = 3, n = 20, is_discrete = F)
image(volcano, col = pal)
```

```{r}
## discrete example
pal <- ondri_palette("Cohort1")
image(volcano, col = pal)
```

## **Usage and examples**

To start let's see the palette colors

```{r}
# See all ONDRI palettes
names(ondri_palettes)
```

### A tidy & ggplot2 example


Here we provide an example with `ggplot2`.


```{r}
library(ggplot2)
library(ondricolors)

data('toy_ONDRI_data')

ggp_color <- ggplot(toy_ONDRI_data, aes(x = X, y = Y, color = COHORT)) +
geom_point() +
scale_color_manual(values = ondri_palette("Cohort2"))

ggp_color


```

### A base R example

And here we provide an example with base `R`

```{r}

library(ondricolors)
data('toy_ONDRI_data')

## for the filled pchs
plot(toy_ONDRI_data$X, toy_ONDRI_data$Y, col = ondri_palette("Cohort2")[as.character(toy_ONDRI_data$COHORT)], pch = 20)

## for the pchs with bgs
plot(toy_ONDRI_data$X, toy_ONDRI_data$Y, bg = ondri_palette("Cohort2")[as.character(toy_ONDRI_data$COHORT)], pch = 21)


```

